Evolution of the AGN UV luminosity function from redshift 7.5

### 2019-02-25 Paper/paper.tex
Update

Our calculation of the AGN contribution to the UV background follows
previous work on UV background synthesis models
\citep[e.g.][]{1996ApJ...461...20H,2012ApJ...746..125H}.  The main
quantity of interest is the \ion{H}{i} photoionization rate of the UV
background
\begin{equation}
  \Gamma_\ion{H}{i}\left(z\right)=\int_{\nu_{912}}^\infty\mathrm{d}\nu
  \frac{4\pi J_\nu\left(\nu,z\right)}{h\nu} \sigma_\ion{H}{i}\left(\nu\right)\quad,
  \label{eqn:gammapi}
\end{equation}
where $h$ is Planck's constant, $\sigma_\ion{H}{i}(\nu)$ is the
\ion{H}{i} photoionization cross-section \citep{1997MNRAS.292...27H,
  2011piim.book.....D}, and
\begin{multline}
  J_\nu(\nu, z)=\frac{c}{4\pi}\int_{z}^\infty\mathrm{d}z^\prime\frac{\left(1+z\right)^3}{H\left(z^\prime\right)\left(1+z^\prime\right)}\epsilon_\nu\left(\nu_\mathrm{em},z^\prime\right)\\
  \times\exp{\left[-\tau_\mathrm{eff}\left(\nu, z, z^\prime\right)\right]}
  \label{eqn:flux}
\end{multline}
is the angle- and space-averaged specific intensity of the UV
background. In the above equation
$H\left(z^\prime\right)=H_0(\Omega_\mathrm{m}\left(1+z^\prime\right)^3+\Omega_\Lambda)^{1/2}$
is the Hubble parameter, and
$\epsilon_\nu\left(\nu_\mathrm{em},z^\prime\right)$ is the comoving
emissivity of all \ion{H}{i} Lyman continuum sources at redshift
$z^\prime>z$ and emitted frequency
$\nu_\mathrm{em}=\nu\left(1+z^\prime\right)/\left(1+z\right)>\nu_{912}$.
In practice, we adopt an upper limit $z^\prime_\mathrm{max}=15$ when
integrating Equation~\eqref{eqn:flux}.  Assuming that quasars are the
only ionizing sources and considering Equation~\eqref{eqn:sed} we have
\begin{equation}
  \epsilon_\nu\left(\nu_\mathrm{em},z^\prime\right) = \epsilon_{912}\left(z^\prime\right)\left(\frac{\nu_\mathrm{em}}{\nu_{912}}\right)^{-1.70}\quad,
  \label{eqn:epsilon_freq}
\end{equation}
with $\epsilon_{912}\left(z^\prime\right)$ obtained as described in
Section~\ref{sec:e912}.  For Poisson-distributed absorbers with an
\ion{H}{i} column density distribution
$f\left(N_\ion{H}{i},z^{\prime\prime}\right)=\partial^2n/\left(\partial
N_\ion{H}{i}\partial z^{\prime\prime}\right)$, the effective optical
depth to \ion{H}{i} Lyman continuum photons travelling between
redshifts $z^\prime$ and $z$ is \citep{1980ApJ...240..387P}
\begin{equation}
  \tau_\mathrm{eff}\left(\nu,z,z^\prime\right) = \int_{z}^{z^\prime}\mathrm{d}z^{\prime\prime}\int_0^\infty
  \mathrm{d}N_\ion{H}{i} f\left(N_\ion{H}{i},z^{\prime\prime}\right)\left[1-e^{-\tau_1}\right]\quad,
   \label{eqn:taueff}
\end{equation}
where $\tau_1\approx
N_\ion{H}{i}\sigma_\ion{H}{i}\nu\left(1+z^{\prime\prime}\right)/\left(1+z\right)$
is the Lyman continuum optical depth through an individual
absorber\footnote{The helium content of the absorber can be ignored
  due to the small \ion{H}{i} photoionization cross section at
  $\lambda<304$\,\AA.}.  For the \ion{H}{i} column density
distribution $f\left(N_\ion{H}{i},z\right)$ we adopt the piecewise
power-law parametrization by \citet{2012ApJ...746..125H} that is
consistent with $f\left(N_\ion{H}{i},z\right)$ measurements at
$z<3.5$, and roughly reproduces both the \ion{H}{i} Ly$\alpha$
effective optical depth \citep[but not in detail---see][]{2015MNRAS.450.4081P,2017MNRAS.464..897B,2017ApJ...837..106O}
and the measured mean free path to \ion{H}{i} Lyman limit photons at
$z<5.5$ \citep{2009ApJ...705L.113P,2014MNRAS.445.1745W}.
\citet{2018arXiv180109693K} suggest that variations in
$f\left(N_\ion{H}{i},z\right)$ result in modest (10--40 per cent)
changes in $\Gamma_\ion{H}{i}$ at $z<3$. We note, however, that at
$z\ga 3.5$ all UV background synthesis models are based on brazen
extrapolations of $f\left(N_\ion{H}{i},z\right)$, whose detailed shape
for (partial) Lyman limit systems is not well constrained at these
redshifts \citep{2010ApJ...718..392P}.

>>>>

Our calculation of the AGN contribution to the UV background follows
previous work on UV background synthesis models
\citep[e.g.][]{1996ApJ...461...20H,2012ApJ...746..125H}.  The main
quantity of interest is the \ion{H}{i} photoionization rate of the UV
background
\begin{equation}
  \Gamma_\ion{H}{i}\left(z\right)=\int_{\nu_{912}}^\infty\mathrm{d}\nu
  \frac{4\pi J_\nu\left(\nu,z\right)}{h\nu} \sigma_\ion{H}{i}\left(\nu\right)\quad,
  \label{eqn:gammapi}
\end{equation}
where $h$ is Planck's constant, $\sigma_\ion{H}{i}(\nu)$ is the
\ion{H}{i} photoionization cross-section \citep{1997MNRAS.292...27H,
  2011piim.book.....D}, and
\begin{multline}
  J_\nu(\nu, z)=\frac{c}{4\pi}\int_{z}^\infty\mathrm{d}z^\prime\frac{\left(1+z\right)^3}{H\left(z^\prime\right)\left(1+z^\prime\right)}\epsilon_\nu\left(\nu_\mathrm{em},z^\prime\right)\\
  \times\exp{\left[-\tau_\mathrm{eff}\left(\nu, z, z^\prime\right)\right]}
  \label{eqn:flux}
\end{multline}
is the angle- and space-averaged specific intensity of the UV
background. In the above equation
$H\left(z^\prime\right)=H_0(\Omega_\mathrm{m}\left(1+z^\prime\right)^3+\Omega_\Lambda)^{1/2}$
is the Hubble parameter, and
$\epsilon_\nu\left(\nu_\mathrm{em},z^\prime\right)$ is the comoving
emissivity of all \ion{H}{i} Lyman continuum sources at redshift
$z^\prime>z$ and emitted frequency
$\nu_\mathrm{em}=\nu\left(1+z^\prime\right)/\left(1+z\right)>\nu_{912}$.
In practice, we adopt an upper limit $z^\prime_\mathrm{max}=7$ when
integrating Equation~\eqref{eqn:flux}.  \new{Due to the short mean
  free path at high redshifts $z^\prime_\mathrm{max}=7$ is sufficient
  to give converged result.  We do not require severe extrapolation of
  our emissivity models to high redshifts.} Assuming that quasars are
the only ionizing sources and considering Equation~\eqref{eqn:sed} we
have
\begin{equation}
  \epsilon_\nu\left(\nu_\mathrm{em},z^\prime\right) = \epsilon_{912}\left(z^\prime\right)\left(\frac{\nu_\mathrm{em}}{\nu_{912}}\right)^{-1.70}\quad,
  \label{eqn:epsilon_freq}
\end{equation}
with $\epsilon_{912}\left(z^\prime\right)$ obtained as described in
Section~\ref{sec:e912}.  For Poisson-distributed absorbers with an
\ion{H}{i} column density distribution
$f\left(N_\ion{H}{i},z^{\prime\prime}\right)=\partial^2n/\left(\partial
N_\ion{H}{i}\partial z^{\prime\prime}\right)$, the effective optical
depth to \ion{H}{i} Lyman continuum photons travelling between
redshifts $z^\prime$ and $z$ is \citep{1980ApJ...240..387P}
\begin{equation}
  \tau_\mathrm{eff}\left(\nu,z,z^\prime\right) = \int_{z}^{z^\prime}\mathrm{d}z^{\prime\prime}\int_0^\infty
  \mathrm{d}N_\ion{H}{i} f\left(N_\ion{H}{i},z^{\prime\prime}\right)\left[1-e^{-\tau_1}\right]\quad,
   \label{eqn:taueff}
\end{equation}
where $\tau_1\approx
N_\ion{H}{i}\sigma_\ion{H}{i}\nu\left(1+z^{\prime\prime}\right)/\left(1+z\right)$
is the Lyman continuum optical depth through an individual
absorber\footnote{The helium content of the absorber can be ignored
  due to the small \ion{H}{i} photoionization cross section at
  $\lambda<304$\,\AA.}.  For the \ion{H}{i} column density
distribution $f\left(N_\ion{H}{i},z\right)$ we adopt the piecewise
power-law parametrization by \citet{2012ApJ...746..125H} that is
consistent with $f\left(N_\ion{H}{i},z\right)$ measurements at
$z<3.5$, and roughly reproduces both the \ion{H}{i} Ly$\alpha$
effective optical depth \citep[but not in detail---see][]{2015MNRAS.450.4081P,2017MNRAS.464..897B,2017ApJ...837..106O}
and the measured mean free path to \ion{H}{i} Lyman limit photons at
$z<5.5$ \citep{2009ApJ...705L.113P,2014MNRAS.445.1745W}.
\citet{2018arXiv180109693K} suggest that variations in
$f\left(N_\ion{H}{i},z\right)$ result in modest (10--40 per cent)
changes in $\Gamma_\ion{H}{i}$ at $z<3$. We note, however, that at
$z\ga 3.5$ all UV background synthesis models are based on brazen
extrapolations of $f\left(N_\ion{H}{i},z\right)$, whose detailed shape
for (partial) Lyman limit systems is not well constrained at these
redshifts \citep{2010ApJ...718..392P}.
